\section{Image Polarimetry in Biomedical Field} \label{sec:chp4-sec5}
Image polarimetry refers to different approaches to describe the propagation of polarized light, its interactions with the optical system, and its medium polarized properties.
The Stokes and Mueller systems are well suited for polarimetry applications, since first they can document the full, partial and un-polarized state of light and second they provide an intensity measure and experimental data.

The Stokes and Mueller polarimetries refer to measuring the Stokes vector and the Mueller matrix, respectively.
These systems can be used either to highlight the different layers of the tissue by showing diffuse light coming from deeper layers and showing the medium response with different polarized conditions (Stokes polarimetry) or to highlight some medium characteristics (Mueller polarimetry).

Although the polarization filters are employed in a \acf{pd} in order to remove any specular reflection of light and capture the backscattered light from deeper levels of the skin, the full potential of image polarimetry in biomedicine has not been explored~\cite{ghosh2011tissue}.
%Gosh~et al.\,\cite{ghosh2011tissue} summarizes 
%Presumably this is due to the challenges such as~\cite{ghosh2011tissue}: 
%	\begin{itemize}
%	\item Extensive loss of polarization signal as a effect of tissue multiple scattering 
%	\item Complicated nature of polarization effects in tissue
%	\item Measurements difficulty, specially for small polarization signals
%	\item Challenges in analysis and quantification of measured signals or images 
%	\item Complexities in understanding and analyzing the obtained results 
%	\item Lack of detailed information on polarimetric properties of various tissues and their effects on polarized propagation.
%	\end{itemize}
	
Currently, several researchers are pursuing innovative solutions in the filed of image polarimetry.
A comprehensive summary of current research in polarimetry and it's problems is provided by Ghosh~et al.\,\cite{ghosh2011tissue}.
%Ghosh~et al.\,\cite{ghosh2011tissue} provided a good summary on the current stage of the research in polarimtery and its problems.
Polarimetry systems can be used either for tissue imaging or analyzing the tissue's optical characteristics.
We categorized the applied polarimetry systems into three groups: (i) partial Stokes polarimeters, (ii) Stokes polarimeters, and (iii) Mueller polarimeters.
The techniques in the first two categories are used to define the polarization state of the backscattered light from the object and the last one is used to detect the optical properties of the sample.
The aforementioned groups and their related studies are discussed in the following.


%However the Stokes-Mueller polarimetry is more suited for polarimetry applications due to two reasons. First the polarized light after interaction with the medium could be fully, partial or un-polarized and Jones calculus is only applicable for fully polarized light state.
%Second intensity measurements of polarized lights and experimental data are more desirable and Mueller formalism is based on experimental consideration of intensity measurements.
%Based on mentioned reasons, the Stokes-Mueller polarimetry is explained in the following. 
% Stokes-Mueller polarimetry system contains two major elements; \textit{PSA}, polarization states analyser and \textit{PSG}, polarization states generator. The \textit{PSA} contains a set of elements which analyse the polarization state of incoming light and \textit{PSG} contains the elements which generate the polarization states. Three main subcategory of polarimetry are introduced by \cite{goldstein2003polarized}, which includes:
%\begin{itemize}
%	\item Rotating element polarimetry \\
%	The Stokes vector and Mueller matrix parameters are measured here with rotating the polarized elements (polarizer, retarder). 	
%	\item Oscillating element polarimetry \\
%	Which rotates the polarization of light using some electro or magneto-optical device such as liquid crystal cell. 
%	\item Phase modulation polarimetry \\
%	These polarimeters use devices that vary in retardance in response to an electrical signal.
%\end{itemize} 
%
%However different types of imaging polarimetry systems had implemented in the literature which does not follow the mentioned category exactly. These systems are discussed with their details in section \ref{polState}.
%\input{Chapter4/ImagePolarimetry-LuChip.tex}

\input{Chapter4/PolarimetrySystemsBiomedical.tex}